Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-10-28 Internal_models/article-models-ttinternal.tex
recovered those lost files

\begin{rmk}\label{rmk:cftwk-prewk}
In this remark we explain what it means that weakening is a pre-weakening
homomorphism. Let $\cftalg{A}$ be a pre-weakening algebra. Then its weakening
$\cftwk{\cftalg{A}}$ is an extension homomorphism from
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}$ to
$\cftfamalg{\cftfamalg{\cftalg{A}}}$. Therefore, $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism if the diagram
\begin{equation*}
\begin{tikzcd}[column sep=8em]
\ctxwk
  {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}
    { \ctxwk
        {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
        {\cftfamhom{\cftwk{\cftalg{A}}}}
      }
  \ar{d}[swap]{\cftwk{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
    {\cftwkc{\cftalg{A}}}
    {\ctxwk{\cftalgf{\cftfamalg{\cftfamalg{\cftalg{A}}}}}{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
  \ar{d}
    { \jcomp{}
        { \cftwkf{\cftalg{A}}}
        { \jcomp{}
            { \cftwkc{\cftalg{A}}}
            { \cftwk{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
      }
  \\
\cftfamalg{\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}[swap]
    { \cftfamhom
        { \cftfamhom
            { \cftwk{\cftalg{A}}}
          }
      }
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
      {\cftwkc{\cftalg{A}}}
      {\cftfamalg{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
\end{tikzcd}
\end{equation*}
of pre-weakening algebras in context
$ \ctxext
    { { { { \Gamma}
          { \cftalgc{\cftalg{A}}}
          }
        { \cftalgf{\cftalg{A}}}
        }
      { \ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      }
    { \cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
      }$
commutes judgmentally.
\end{rmk}

@@

Thus we may conclude that the diagram above a pullback of the diagram in \autoref{diag:cftwk-cftwk}

@@

\subsection{Pre-universes}
Pre-universes are internal versions of the theory of contexts, families and
terms. They interpret extension, the empty context, weakening, substitution
and identity terms all at once in a compatible way. Besides the compatibility
properties there will be judgmental equalities analogous to the cancellation
properties of \autoref{cancellation-ws,cancellation-i}. Pre-universes are to
the theory of contexts, families and terms what internal categories to a
category.

>>>>

\begin{rmk}\label{rmk:cftwk-prewk}
In this remark we explain what it means that weakening is a pre-weakening
homomorphism. Let $\cftalg{A}$ be a pre-weakening algebra. Then its weakening
$\cftwk{\cftalg{A}}$ is an extension homomorphism from
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}$ to
$\cftfamalg{\cftfamalg{\cftalg{A}}}$. Therefore, $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism if the diagram
\begin{equation*}\label{diag:cftwk-cftwk}
\begin{tikzcd}[column sep=8em]
\ctxwk
  {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}
    { \ctxwk
        {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
        {\cftfamhom{\cftwk{\cftalg{A}}}}
      }
  \ar{d}[swap]{\cftwk{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
    {\cftwkc{\cftalg{A}}}
    {\ctxwk{\cftalgf{\cftfamalg{\cftfamalg{\cftalg{A}}}}}{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
  \ar{d}
    { \jcomp{}
        { \cftwkf{\cftalg{A}}}
        { \jcomp{}
            { \cftwkc{\cftalg{A}}}
            { \cftwk{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
      }
  \\
\cftfamalg{\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}[swap]
    { \cftfamhom
        { \cftfamhom
            { \cftwk{\cftalg{A}}}
          }
      }
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
      {\cftwkc{\cftalg{A}}}
      {\cftfamalg{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
\end{tikzcd}
\end{equation*}
of pre-weakening algebras in context
$ \ctxext
    { { { { \Gamma}
          { \cftalgc{\cftalg{A}}}
          }
        { \cftalgf{\cftalg{A}}}
        }
      { \ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      }
    { \cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
      }$
commutes judgmentally.
\end{rmk}

@@

Thus we may conclude that the diagram above is a pullback of the diagram in \autoref{diag:cftwk-cftwk}

@@
